\documentclass[a4paper]{article}

\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage[empty]{fullpage}
\usepackage{titling}
% \usepackage{fontspec}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.45in}
\addtolength{\textheight}{1in}
\setlength{\headheight}{18pt}
\setlength{\footskip}{3.7pt}
\setlength{\tabcolsep}{0in}
\setcounter{secnumdepth}{-\maxdimen}
% \setmonofont[Contextuals=Alternate]{Fira Code}
\urlstyle{rm}
% \raggedbottom
% \raggedright

\title{Omri Bornstein's CV}
\author{Omri Bornstein}
\date{\today}
\hypersetup{
	pdftitle={\thetitle},
	pdfauthor={\theauthor},
	bookmarksnumbered=true,
	bookmarksopen=true,
	bookmarksopenlevel=1,
	colorlinks=true,
	pdfstartview=Fit,
	pdfpagemode=UseOutlines,
	colorlinks=true,
	allcolors=blue
}
\pagestyle{fancy}
\fancyhf{}
\lhead{\href{mailto:omribor@gmail.com}{omribor@gmail.com}}
\chead{\Large Omri Bornstein}
\rhead{\href{https://applegamer22.github.io}{applegamer22.github.io}}

\begin{document}
	\section{Education}

	\begin{enumerate}
		\item \textbf{2017 - 2019}: secondary education at Australian Science \& Mathematics School, Adelaide, South Australia
		\item \textbf{2020 - Present}: Bachelor of Computer Science at Monash University, Melbourne, Victoria
	\end{enumerate}

	\section{Skills}

	\begin{itemize}
		\item \textbf{Computer Programming Languages}: \href{https://go.dev}{Go}, TypeScript/JavaScript, Python, Kotlin/Java, C/C++
		\item \textbf{Document Markup Languages}: HTML/CSS, \TeX, Markdown
		\item \textbf{Natural Languages}: English, Hebrew
		\item \textbf{Tools}: Git, GitHub, Docker, Kubernetes, \href{https://goreleaser.com}{GoReleaser}, \href{https://github.com/features/actions}{GitHub Actions}
		\item \textbf{Platforms}: Linux, Cloud Native, Web
		\item \textbf{Soft Skills}: Writing, Presenting, Collaboration
	\end{itemize}

	\section{Experience}

	\begin{enumerate}
		\item \textbf{May 2021 - January 2022}: General Representative at Monash University Cyber Security Club (MonSec).
		\item \textbf{January 2022 - June 2022}: Secretary at Monash University Cyber Security Club (MonSec).
		\item \textbf{June 2022 - Present}: Vice President at Monash University Cyber Security Club (MonSec).
	\end{enumerate}

	\section{Projects}
	\subsection{Open-Source}

	\begin{itemize}
		\item \href{https://github.com/AppleGamer22/cocainate}{\texttt{cocainate}} is a cross-platform re-implementation of the macOS utility \href{https://github.com/apple-oss-distributions/PowerManagement/tree/main/caffeinate}{\texttt{caffeinate}} that keeps the screen turned on either until stopped, for a set duration of time or while another process still runs.
		\item \href{https://github.com/AppleGamer22/stalk}{\texttt{stalk}} is a cross-platform file-watcher that can run a command after each file-system operation on a given file(s) or simply wait once until a file is changed.
		\item \href{https://github.com/AppleGamer22/rake}{\texttt{rake}} is a social media scraper that is interfaced via a server-side rendered HTML user interface (or a CLI), and is managed by a REST API and a NoSQL database.
		\item \href{https://github.com/AppleGamer22/scr-web}{scr-web} (and its \href{https://github.com/AppleGamer22/scr-cli}{scr-cli} counterpart) is my previous attempt at building a full-stack social media scraper, which was abandoned due to the excessive number of dependencies and the rather large build-size.
		\item \href{https://github.com/AppleGamer22/sp}{sp} is my first attempt at building a Minecraft server plugin. This plugin adds the requirement that the player supplies the password (via a server command) before proper server interaction is allowed. Until as password is provided, the currently-unauthorized player is blinded and immobile.
	\end{itemize}

	\subsection{Research}
	\begin{itemize}
		\item As part of the \href{https://handbook.monash.edu/2021/units/FIT2082}{FIT2082 unit}, I \href{https://github.com/AppleGamer22/FIT2082}{contributed} to an existing codebase, based on prior research by \href{https://ojs.aaai.org/index.php/ICAPS/article/view/3471}{(Gange, Harabor and Stuckey, 2021)} about \textsl{Lazy CBS}, their Multi-Agent Path Finding (\textsl{MAPF}) algorithm. The \textsl{MAPF} problem is a subset of the path finding research field, which presents the additional requirements of multiple agents, each with a unique pair of a source and a target, such that the path between them does not intersect with another path during the same point in time. My task was to modify the \textsl{Lazy CBS} codebase such that the algorithm also outputs the final set of constraints that is used to rule out possible paths, such that the Lazy is formally an Explainable Multi-Agent Path Finding (\textsl{XMAPF}) algorithm. In addition, I added \href{https://pybind11.readthedocs.io/en/stable/}{\textsl{Python}-to-\textsl{C++} bindings}, such that the compiled \textsl{Lazy CBS} codebase can be used as a Python-facing library for future projects.
	\end{itemize}

	\subsection{Freelancing}
\end{document}